Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2025-02-25 Paper.tex
Xi theta return order

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code\footnote{During initialization code execution, \texttt{EXTCODESIZE} on the address should return zero, which is the length of the code of the account while \texttt{CODESIZE} should return the length of the initialization code (as defined in \ref{subsec:instruction-set}).}. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SELFDESTRUCT} instruction, the matter is moot since the account will be deleted before the transaction is completed. For a normal {\small STOP} code, or if the code returned is otherwise empty, then the state is left with a zombie account, and any remaining balance will be locked into the account forever.

>>>>

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code\footnote{During initialization code execution, \texttt{EXTCODESIZE} on the address must return zero, which is the length of the code of the account while \texttt{CODESIZE} should return the length of the initialization code (as defined in \ref{subsec:instruction-set}).}. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SELFDESTRUCT} instruction, the matter is moot since the account will be deleted before the transaction is completed. For a normal {\small STOP} code, or if the code returned is otherwise empty, then the state is left with a zombie account, and any remaining balance will be locked into the account forever.
